The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Add really exciting figure!!

>>>>

\subsection{Line-intensity mapping} \label{ssec:lim}
We now turn to understanding how \zst{} depends on the parameters of our
generic line-intensity mapping field: the slope ($\alpha$) and lognormal
scatter ($\sigma$). See \S~\ref{ssec:oiii_int_map} for more details of the
construction of the field.

In Fig.~\ref{fig:ztran_vs_alpha_sigma} we plot \zst{} as a function of each of
these parameters\,--\,$\alpha$ and $\sigma$. We see that \zst{} is remarkably
insensitive to the value of either of these parameters, with some small
deviation as a function of $\alpha$. The \hot{}, \fid{}, and \cold{} models
only vary by a total of $1.2\%$, $0.56\%$, $0.52\%$ with respect to $\alpha$,
and $0.070\%$, $0.10\%$, and $0.11\%$ with respect to $\sigma$, respectively.

\begin{figure*}
\includegraphics[width=\textwidth]{plots/ztran_vs_alpha_sigma.pdf}
\caption{The transition redshift (\zst) defined by cross-correlating with a
generic two-parameter intensity mapping field. The parameter $\alpha$ sets the
slope of the luminosity-mass relation and the parameter $\sigma$ sets the
lognormal scatter in this relation (see \S~\ref{ssec:oiii_int_map}). The
\hot{}, \fid{}, and \cold{} models only vary by a total of $1.2\%$, $0.56\%$,
$0.52\%$ with respect to $\alpha$, and $0.070\%$, $0.10\%$, and $0.11\%$ with
respect to $\sigma$, respectively. Clearly \zst{} varies only with the
structure of the 21~cm field, and is thus an excellent probe of reionization.}
\label{fig:ztran_vs_alpha_sigma}
\end{figure*}
